\documentclass[./main.tex]{subfiles}

\begin{document}
The SANS (SysAdmin, Audit, Network and Security) Institute defines an intrusion detection as “the act of detecting actions that attempt to compromise the confidentiality, or availability of a resource” (SANS Institute). There are three main categories to intrusion detection systems: network based, host based, and physical. This research primarily focuses on network and host based intrusion detection and analysis using applications and services such as Bro, Tripwire, Fail2Ban, and software to analyze the logs they generate.

Network intrusions are an increasingly common occurrence which happen every second on cloud based systems. The affordability and ease of use has made cloud hosting an incredibly popular choice. However, this also allows both experienced system administrators who have a solid understanding of security and everyone else to share the same resource pool. This situation is comparable to having someone who just got their license to drive on the busiest highway in the world during rush hour traffic while in inclement weather. Statistically, there will be many accidents due to inexperience, just as there will be many vulnerable systems occupying resource pools with hundreds of other virtual machines on them. Naturally, this affects everyone using the service, just as a traffic accident causes disarray to overpopulated highways during rush hour traffic. This endangers the resiliency of cloud security in many ways and poses a challenge for businesses who provide cloud hosting and to those who use it as a service. 

\end{document}
